---
title: "Author Name Change Policies by Publishers included in PubMed"
format: html
editor: visual
---

## Abstract

```{r}
#| echo: false
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(ggplot2))
suppressPackageStartupMessages(library(plotly))
suppressPackageStartupMessages(library(formattable))
suppressPackageStartupMessages(library(DT))
```

## Background

In 2021, the Trans Name Change Policy Working Group (NCPWG) authored a article for the Committee for Publishing Ethics (COPE) that outlined their vision for "a more trans inclusive publishing world" (Tannenbaum et al, 2021). In the article, the group detailed barriers to receiving full credit for their academic work and offered guiding principles for what an inclusive name change policy should look like.

The principles discussed in the article are as follows:

> Accessibility - Name changes should be available to authors upon request without legal documentation, unnecessary barriers, burdens, or labor placed upon the author making the request.
>
> Comprehensiveness - Name changes should remove all instances of an author's previous name from the records maintained and disseminated by the publisher.
>
> Invisibility - Name changes should not draw attention to the gender identity of an author, nor create a clear juxtaposition between the current name and the previous name.
>
> Expediency and Simplicity - Name changes should be implemented in a timely manner, and with a minimum of bureaucratic overhead.
>
> Recurrence and Maintenance - Publishers should regularly audit and correct new instances of changed names in order to prevent ongoing dissemination of incorrect information.
>
> (Tannenbaum et al, 2021)

While both the COPE and the National Information Standards Organization (NISO) formed working groups to develop recommended practice in relation to the changing of author names post-publication in the academic record, neither group has released official recommendations as of the beginning of 2023. Still, the past three years have seen a proliferation of publisher-driven development of name change policies for their journals.

With the growing presence of name change policies in mind, this paper seeks to better understand how health science publishers, databases, and other organizations are handling author name changes and the extent of the presence of these policies in the health publishing landscape.

## Methodology

### Scope

The data acquired for analysis for this survey focuses on the content of indexed in PubMed (including Medline) and the full-text database PubMed Central. It was acquired through querying the National Center for Biotechnology Information's xxxxxxx for data providing entities that contribute to the service. These data providers can be publishing companies as well as \[Silverchair, etc.\]

In order to create a more manageable search and to reflect the researcher's linguistic capabilities, the list of publishers to search was limited to those that included English in their names. The list was also limited to current contributors of citations to the PubMed landscape. Lastly, publishers that provided data separately but are members of a publishing group or are a subsidiary of a larger publisher that provides data to PubMed were combined into their larger body with the assumption that policies at the higher level apply to their subsidiaries.

A total of 931 publishing bodies were included as part of the data.

### Policy Identification

Following the identification of publishers included in PubMed, a search was conducted for whether each publisher has published a name change policy.

The process for searching for these policies involved the identification of a search string that would effectively identify a publisher's policy page if extant and the use of the string for every publisher. The terms that were selected were the publishers name, "journal," and "name change policy."

In the Google search browser, executed searches share the same URL format, varying only in the text to be searched. To streamline the process of conducting the search for each publisher, once the terms to be added to the search were identified, OpenRefine was used to take the names of each publisher and include them in a URL that would lead to the search results.

After the URLs were created, they were opened by hand and the results of the search were cataloged for later analysis.

In acknowledgement of the fact that not all policies include the phrase "name change policy" in their documentation, if no results were returned as part of the initial search results, the publisher was added to a list for secondary searching. In addition to no-result publishers, following the initial identification of publishing bodies with name change policies, additional publishers were added to this secondary searching list in coordination with the PubMed team based on the weighted presence of publishers in PubMed. Following the creation of this secondary list, one new search strings was created to attempt to identify the possible presence of a policy: publishers name, "author name" AND "policy." In addition to this search string, the policy webpages of these publishers were hand searched for potential policies.

A total of 39 publishers were identified as having some form of name change policy.

### Policy Features

Once the publishers with policies were identified, they underwent a content analysis that was based on the principles put forth by the NCWG.

Each policy was read at least twice and assessed for their adherence to concepts of accessibility, comprehensiveness, invisibility, expediency and simplicity, and recurrence and maintenance.

What emerged from this analysis was the identification of common features that were included in these policies, which then became the basis for the criteria chosen to compare the policies as part of this work. The criteria documented about the policies are as follows:

**Invisibility**

-   Invisible Option - Does the publisher offer the ability to change an author's name without the publication of an erratum, correction, or other type of notice?

-   Mention of co-authors or corresponding authors - Does the publisher mention the contacting of co-authors or corresponding authors? If so, is it a requirement that someone outside of the author and the publisher themselves be contacted?

**Comprehensiveness**

-   Pronouns - Does the policy include mention of the ability to change pronouns?

-   Photos - Does the policy include mention of the ability to change associated photos?

-   Email - Does the policy include mention of the ability to change associated email?

**Expediency and Simplicity**

-   Proof of Change - Does the publisher require proof of name change?

-   Confirmation of Identify - Does the publisher require proof of identify? If so, to what level of proof do they require?

-   Method of request - How does the publisher require the author to initiate a name change?

**Recurrence and maintenance**

-   Mention of the Internal Retention of Data - Does the publisher mention whether or not the initial name under which the article was published will be retained in their data or not?

-   Updating past citations - Does the publisher mention/offer to update past citations of the paper to reflect the new name?

-   Provision of updated data to indexing services - Does the publisher mention whether they will reserve the article's data to indexing services?

### Policy Analysis

Following policy related data collection, findings were collected and tallied in a single spreadsheet. Using xxxx data provided by the, corresponding journal totals for each publisher were identified and added to the spreadsheet to be included as part of the analysis.

A total of 6267 journals were included as part of the data.

Data analysis and visualization were performed in Microsoft Excel and R.

## Findings

### Policy Pervasiveness

```{r}
#| echo: false
policyfeatures <- tribble(
~category, ~journals,	~publishers,
"Total",	6267,	931,
"No Policy",	2017,	892,
"Has Policy",	4250,	39,
"Invisible Option",	4238,	37,
"Co-authors",	1768,	26,
"Pronouns",	992,	16,
"Photos",	105,	7,
"Email",	272,	11,
"ID Confirmation",	347,	11,
"Email to Update",3141,26,
"Form to Update",450,9,
"Insufficient update instructions",659,4,
"Internal Data Retention",	274,	10,
"Databases",	4120,	34,
"Updates In-House Publication Citations",115,3,
"Notes No Citation Update",330,9,
"Mentions Future Citation Goals",200,3,
"Mentions COPE Name Change Guidelines",3157,8,
"Mentions COPE",3558,11
)
```

```{r}
#| echo: false
haspolicypie <- plot_ly()
haspolicypie <- haspolicypie %>%
  add_pie(
    labels = c("No Policy", "Has Policy"),
    values = c(2017,4250),
    name = "Journals",
    domain = list(row = 0, column = 0),
    textinfo="percent")
haspolicypie <- haspolicypie %>%
  add_pie(
    labels = c("No Policy", "Has Policy"),
    values = c(894,39),
    name = "Publishers",
    domain = list(row = 0, column = 1),
        textinfo="percent")

haspolicypie <- haspolicypie %>% layout(title = "Status of Name Change Policies <br> Applying to Journals and Corresponding Publishers <br> in PubMed", showlegend = T,
                      grid=list(rows=1, columns=2),
                      xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
                      yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE))

annotations = list( 
  list( 
    x = 0.23,  
    y = .1,  
    text = "Journals",  
    xref = "paper",  
    yref = "paper",  
    xanchor = "center",  
    yanchor = "bottom",  
    showarrow = FALSE 
  ),  
  list( 
    x = 0.76,  
    y = .1,  
    text = "Publishers",  
    xref = "paper",  
    yref = "paper",  
    xanchor = "center",  
    yanchor = "bottom",  
    showarrow = FALSE 
  ))

haspolicypie <- haspolicypie %>%layout(annotations = annotations) 

haspolicypie
```

```{r}
#| echo: false
top10<- tribble(
  ~publisher,~journals,~policy,
"Elsevier",1365,TRUE,
"Wiley",1023,TRUE,
"Springer Nature",512,TRUE,
"Oxford",	339,TRUE,
"Sage",	144,TRUE,
"Karger",	134,FALSE,
"Lippincott, Williams & Wilkins",	128,TRUE,
"Bentham",	97,FALSE,
"IEEE",	93,TRUE,
"Dove",73,TRUE)

top10 <- top10 %>%
  mutate(percent=journals/6267)


top10_table<-formattable(top10,
            align = c("l", rep("r", NCOL(top10) - 1)),
            list(
              `policy`=formatter("span",
    style = x ~ style(color = ifelse(x, "green", "red")),
    x ~ icontext(ifelse(x, "ok", "remove"), ifelse(x, "Yes", "No"))),
              `percent` = percent)
)
```

```{r}
#| echo: false
top10tree <- plot_ly(
  type='treemap',
  labels=c("Has Policy", "Other Publishers (With Policy)", "Elsevier" ,      "Wiley"    ,      "Springer Nature", "Oxford"     ,    "Sage"    ,       "Karger" ,     "Lippincott"  ,   "Bentham"    ,    "IEEE"     ,      "Dove"     ,      "Other Publishers (No Policy)", "No Policy"  ),
  parents=c("", "Has Policy", "Has Policy", "Has Policy", "Has Policy" ,"Has Policy", "Has Policy", "No Policy", "Has Policy" ,"No Policy" ,"Has Policy", "Has Policy", "No Policy",""),
    values=c(0,573,1365, 1023 , 512  ,339,  144 , 134 , 128,   97  , 93,   73,1786,0),
  textinfo="label+value"
)

top10tree
```

### Policy Features

#### Invisibility

```{r}
#| echo: false
policyfeatures_bar<- policyfeatures%>% slice(4:5)
fig1 <-  plot_ly(policyfeatures_bar,
                 y=~category,
                 x=~journals,
                 type='bar',
                 name='Journals',
                 texttemplate="%{label}: %{value}")
fig2 <- plot_ly(policyfeatures_bar,
                y=~category,
                x=~publishers,
                type='bar',
                name='Publishers',
                texttemplate="%{label}: %{value}")
fig <- subplot(fig1,fig2)%>%
  layout(title="Comparing Journal vs Publisher Policy Feature Frequency:<br>Invisibility",
         yaxis = list(
                     zerolinecolor = '#ffff',
                     zerolinewidth = 2,
                     gridcolor = 'ffff',
                     showticklabels=FALSE),
                  yaxis2 = list(
                     zerolinecolor = '#ffff',
                     zerolinewidth = 2,
                     gridcolor = 'ffff',
                     showticklabels=FALSE))

fig
```

#### Comprehensiveness

```{r}
#| echo: false
policyfeatures_comp<- policyfeatures%>% slice(6:8)
fig7 <-  plot_ly(policyfeatures_comp,
                 y=~category,
                 x=~journals,
                 type='bar',
                 name='Journals',
                 texttemplate="%{label}: %{value}")
fig8 <- plot_ly(policyfeatures_comp,
                y=~category,
                x=~publishers,
                type='bar',
                name='Publishers',
                texttemplate="%{label}: %{value}")
comprehensiveness <- subplot(fig7,fig8)%>%
  layout(title="Comparing Journal vs Publisher Policy Feature Frequency:<br> Comprehensiveness",
         yaxis = list(
                     zerolinecolor = '#ffff',
                     zerolinewidth = 2,
                     gridcolor = 'ffff',
                     showticklabels=FALSE),
                  yaxis2 = list(
                     zerolinecolor = '#ffff',
                     zerolinewidth = 2,
                     gridcolor = 'ffff',
                     showticklabels=FALSE))

comprehensiveness
```

#### Expediency and Simplicity

```{r}
#| echo: false
policyfeatures_exp<- policyfeatures%>% slice(10:12)
fig3 <-  plot_ly(policyfeatures_exp,
                 y=~category,
                 x=~journals,
                 type='bar',
                 name='Journals',
                 texttemplate="%{label}: %{value}")
fig4 <- plot_ly(policyfeatures_exp,
                y=~category,
                x=~publishers,
                type='bar',
                name='Publishers',
                texttemplate="%{label}: %{value}")
expediency <- subplot(fig3,fig4)%>%
  layout(title="Comparing Journal vs Publisher Policy Feature Frequency:<br>Expediency and Simplicity",
         yaxis = list(
                     zerolinecolor = '#ffff',
                     zerolinewidth = 2,
                     gridcolor = 'ffff',
                     showticklabels=FALSE),
                  yaxis2 = list(
                     zerolinecolor = '#ffff',
                     zerolinewidth = 2,
                     gridcolor = 'ffff',
                     showticklabels=FALSE))

expediency
```

#### Recurrence and Maintenance

```{r}
#| echo: false
policyfeatures_rec<- policyfeatures%>% slice(13:15)
fig5<-  plot_ly(policyfeatures_rec,
                 y=~category,
                 x=~journals,
                 type='bar',
                 name='Journals',
                 texttemplate="%{label}: %{value}")
fig6 <- plot_ly(policyfeatures_rec,
                y=~category,
                x=~publishers,
                type='bar',
                name='Publishers',
                texttemplate="%{label}: %{value}")
recurrence <- subplot(fig5,fig6)%>%
  layout(title="Comparing Journal vs Publisher Policy Feature Frequency:<br>Recurrence and Maintenance",
         yaxis = list(
                     zerolinecolor = '#ffff',
                     zerolinewidth = 2,
                     gridcolor = 'ffff',
                     showticklabels=FALSE),
                  yaxis2 = list(
                     zerolinecolor = '#ffff',
                     zerolinewidth = 2,
                     gridcolor = 'ffff',
                     showticklabels=FALSE))

recurrence
```

### Policies Over Time

```{r}
#| echo: false
implementationyear<-tribble(
  ~year,~journals,~publishers,
  "2019",12,1,
  "2020",1111,8,
  "2021",2186,12,
  "2022",120,3,
  "unknown",821,15
)

implementationyear <-implementationyear %>%
  mutate(journals_pct=journals/4250*100)%>%
  mutate(publishers_pct=publishers/39*100)
```

```{r}
#| echo: false
progress <- tribble(~"type",~"unknown",~"Y2019",~"Y2020",~"Y2021",~"Y2022",
"journals",19.3,.3,26.2,51.4,2.8,
"publishers",38.5,2.6,20.5,30.8,7.7
)

implementation <- plot_ly(progress, y = ~type, x = ~Y2019, type = 'bar', name = '2019')
implementation <- implementation %>% add_trace(x = ~Y2020, name = '2020')
implementation <- implementation %>% add_trace(x = ~Y2021, name = '2021')
implementation <- implementation %>% add_trace(x=~Y2022, name="2022")
implementation <- implementation %>% add_trace(x=~unknown, name='unknown date')
implementation <- implementation %>% layout(title = "Policy Implementation Coverage by Year",
  yaxis= list(title=''),
  xaxis = list(title = 'Percent of Policy-Applicable Corpus'), barmode = 'stack')


implementation
```

## Discussion

Unique features of certain policies

-   Sage's take on principles of

-   Limited number of publishers offering citation updates

-   Several publishers offer a variety of options for silent vs. in-print changes

    -   More options = more freedom

    -   Are librarians prepared to address this in our own information architecture?

Lack of alignment with underlying principles

-   'Calling out' trans and nb authors and making the policy only available to them is ultimately harmful in its own way.

    -   Having a policy that makes at-risk cases 'special' inherently heightens/highlights that risk rather than diffusing it

        -   Springer nature

-   Lack of clear instructions and ambiguity of what will and won't be changed might make it seem like an open policy, but it also leaves a lot of potential anxiety and unknowns around how a name change request that asks for more than a name will be received by the publisher

-   Contact of co-authors/corresponding authors

    -   Most publishers mention it

-   Inclusion of mention of data retention - ultimate transparency

How can medical librarians prepare scholars who are looking to change the version of record and also how can they advocate for inclusive policies

-   journals such as JMLA should develop policies

-   creating libguides that help point to relevant resources

-   advocate for these principles within institutional repositories

-   advocacy within publishing engagement

Discussion question: What are the roles of health librarians and informationists in developing and facilitating an inclusive publishing environment?

## Limitations

## Conflicts of Interest

## Acknowledgement

## Bibliography

## Appendix A: Publisher Policy Features Table

```{r}
#| echo: false
policytable <- tribble(
~"Name",~"# of Journals",~"Date Instigated",~"Invisible Option",~"Co-authors",~"Pronouns",~"Photos",~"Email",~"ID Confirmation",~"Update Format",~"Internal Data Retention",~"Databases",~"Citation Updates",~"Mentions COPE",~"Notes",
"Elsevier",1365,2021,TRUE,FALSE,FALSE,FALSE,FALSE,FALSE,"EMAIL",FALSE,TRUE,NA,TRUE,NA,
"Wiley",1023,2020,TRUE,TRUE,FALSE,FALSE,FALSE,FALSE,"EMAIL",FALSE,TRUE,NA,TRUE,NA,
"Springer Nature",512,2021,TRUE,FALSE,TRUE,FALSE,FALSE,FALSE,NA,FALSE,TRUE,NA,TRUE,NA,
"Oxford University Press",339,NA,TRUE,FALSE,FALSE,FALSE,FALSE,FALSE,"EMAIL",FALSE,TRUE,NA,TRUE,"Policy mentions COPE generally but does not cite the name change policy guidance.",
"SAGE Publishing",144,2021,TRUE,TRUE,FALSE,FALSE,FALSE,FALSE,"FORM",FALSE,TRUE,FALSE,TRUE,"Acknowledges that it does not currently update citations but mentions working towards being able to do so in the future.",
"Lippincott, Williams & Wilkins",128,NA,TRUE,TRUE,FALSE,FALSE,FALSE,TRUE,NA,FALSE,TRUE,NA,FALSE,NA,
"IEEE",93,NA,TRUE,TRUE,TRUE,FALSE,TRUE,FALSE,"FORM",TRUE,TRUE,TRUE,TRUE, "Will only update citations in IEEE publications",
"Dove Medical Press",73,NA,TRUE,FALSE,TRUE,FALSE,FALSE,FALSE,"FORM",FALSE,TRUE,NA,FALSE, NA,
"BMJ (British Medical Association)",67,2021, TRUE,TRUE,TRUE,FALSE,TRUE,TRUE,"EMAIL",TRUE,TRUE,FALSE,FALSE,NA,
"Taylor & Francis",66,NA,TRUE,FALSE,TRUE,FALSE,FALSE,FALSE,"EMAIL",FALSE,TRUE,NA,FALSE,NA,
"Frontiers",64,2022,TRUE,TRUE,TRUE,FALSE,FALSE,FALSE,"FORM",FALSE,TRUE,NA,FALSE,NA,
"Cambridge University Press", 60,NA,TRUE,FALSE,FALSE,FALSE,FALSE,TRUE,"EMAIL",FALSE,FALSE,NA,FALSE,NA,
"De Gruyter",53,2022,TRUE,TRUE,FALSE,FALSE,FALSE,FALSE,"EMAIL",TRUE,TRUE,NA,TRUE,"COPE guidance is mentioned in a blog post about the policy but not in the language of the policy itself.",
"American Chemical Society",47,2021,TRUE,TRUE,TRUE,TRUE,TRUE,TRUE,"FORM",FALSE,TRUE,FALSE,FALSE,"Acknowledges that it does not currently update citations but mentions working towards being able to do so in the future.",
"American Psychological Association",42,2020,TRUE,TRUE,FALSE,FALSE,FALSE,FALSE,"EMAIL",FALSE,FALSE,NA,FALSE,NA,
"Royal Society of Chemistry",27,2020,TRUE,FALSE,TRUE,TRUE,TRUE,FALSE,"EMAIL",TRUE,TRUE,FALSE,FALSE,NA,
"Mary Ann Liebert",16,NA,TRUE,TRUE,FALSE,FALSE,FALSE,TRUE,"EMAIL",FALSE,FALSE,NA,FALSE,NA,
"American Medical Association",14,NA,TRUE,TRUE,FALSE,FALSE,FALSE,FALSE,NA,FALSE,TRUE,NA,FALSE,NA,
"IOP Publishing",14,2021,TRUE,TRUE,TRUE,TRUE,TRUE,FALSE,"FORM",FALSE,TRUE,FALSE,FALSE,NA,
"Association for Computing Machinery",12,2019,TRUE,FALSE,FALSE,FALSE,FALSE,TRUE,"EMAIL",TRUE,TRUE,TRUE,FALSE,"Will only update citations in ACM publications",
"MIT Press",10,NA,NA,FALSE,FALSE,FALSE,FALSE,FALSE,"EMAIL",FALSE,FALSE,NA,FALSE,NA,
"Ubiquity Press",10,2021,TRUE,TRUE,FALSE,FALSE,FALSE,TRUE,"FORM",TRUE,TRUE,TRUE,TRUE,"Only offers updating citations within the articles in question.",
"American Institute of Physics",9,2021,TRUE,TRUE,FALSE,FALSE,FALSE,FALSE,"EMAIL",FALSE,TRUE,FALSE,FALSE,"Acknowledges that it does not currently update citations but mentions working towards being able to do so in the future.",
"Public Library of Science (PLoS)",9,2020,TRUE,FALSE,FALSE,FALSE,FALSE,FALSE,"EMAIL",FALSE,TRUE,NA,TRUE,"Policy mentions COPE generally but does not cite the name change policy guidance.",
"EDP Sciences",8,NA,TRUE,TRUE,TRUE,TRUE,TRUE,FALSE,"EMAIL",FALSE,TRUE,FALSE,TRUE,NA,
"Future Science Group",8,2021,TRUE,TRUE,FALSE,FALSE,FALSE,FALSE,"EMAIL",FALSE,TRUE,NA,FALSE,NA,
"American Physiological Society",6,2021,TRUE,TRUE,FALSE,FALSE,FALSE,FALSE,"EMAIL",FALSE,TRUE,NA,FALSE,NA,
"Company of Biologists",5,2021,TRUE,TRUE,TRUE,TRUE,TRUE,FALSE,"EMAIL",TRUE,TRUE,NA,FALSE,NA,
"Emerald Group Publishing",5,2020,TRUE,FALSE,TRUE,FALSE,FALSE,FALSE,NA,FALSE,TRUE,NA,FALSE,NA,
"Optical Society of America",5,NA,TRUE,TRUE,TRUE,FALSE,TRUE,FALSE,"EMAIL",FALSE,TRUE,FALSE,FALSE,NA,
"Rockefeller University Press",3,NA,TRUE,TRUE,FALSE,FALSE,FALSE,FALSE,"FORM",TRUE,TRUE,FALSE,FALSE,NA,
"Copernicus Publications",3,2022,TRUE,TRUE,FALSE,FALSE,FALSE,FALSE,"EMAIL",FALSE,TRUE,FALSE,FALSE,NA,
"American Society for Microbiology",2,2020,TRUE,TRUE,TRUE,FALSE,TRUE,TRUE,"EMAIL",FALSE,TRUE,FALSE,FALSE,NA,
"IOS Press",2,NA, FALSE,FALSE,FALSE,FALSE,FALSE,FALSE,"FORM",FALSE,FALSE,NA,TRUE,NA,
"PeerJ Publishing",2,2021,TRUE,TRUE,FALSE,FALSE,FALSE,FALSE,"EMAIL",FALSE,TRUE,NA,FALSE,NA,
"Radiological Society of North America",2,NA,TRUE,TRUE,TRUE,TRUE,TRUE,TRUE,"EMAIL",FALSE,TRUE,NA,FALSE,NA,
"Royal Society",2,NA,TRUE,FALSE,TRUE,TRUE,TRUE,FALSE,"EMAIL",TRUE,TRUE,NA,FALSE,NA,
"Wellcome Trust",2,2020,TRUE,TRUE,FALSE,FALSE,FALSE,TRUE,"EMAIL",TRUE,TRUE,NA,FALSE,NA,
"eLife Sciences Publications",1,2020,TRUE,TRUE,FALSE,FALSE,FALSE,TRUE,"EMAIL",FALSE,TRUE,FALSE,FALSE,NA
)

formattable(policytable,
            align = c("l", rep("r", NCOL(top10) - 1)),
            list(`Date Instigated`= color_tile("lightpink", "lightblue"),
                `# of Journals`=color_tile("whitesmoke","plum"),
              `Invisible Option`=formatter("span",
    style = x ~ style(color = ifelse(x, "green", "red")),
    x ~ icontext(ifelse(x, "ok", "remove"), ifelse(x, "Yes", "No"))),
    `Co-authors`=formatter("span",
    style = x ~ style(color = ifelse(x, "green", "red")),
    x ~ icontext(ifelse(x, "ok", "remove"), ifelse(x, "Yes", "No"))),
    `Pronouns`=formatter("span",
    style = x ~ style(color = ifelse(x, "green", "red")),
    x ~ icontext(ifelse(x, "ok", "remove"), ifelse(x, "Yes", "No"))),
    `Photos`=formatter("span",
    style = x ~ style(color = ifelse(x, "green", "red")),
    x ~ icontext(ifelse(x, "ok", "remove"), ifelse(x, "Yes", "No"))),
    `Email`=formatter("span",
    style = x ~ style(color = ifelse(x, "green", "red")),
    x ~ icontext(ifelse(x, "ok", "remove"), ifelse(x, "Yes", "No"))),
    `ID Confirmation`=formatter("span",
    style = x ~ style(color = ifelse(x, "green", "red")),
    x ~ icontext(ifelse(x, "ok", "remove"), ifelse(x, "Yes", "No"))),
    `Internal Data Retention`=formatter("span",
    style = x ~ style(color = ifelse(x, "green", "red")),
    x ~ icontext(ifelse(x, "ok", "remove"), ifelse(x, "Yes", "No"))),
    `Databases`=formatter("span",
    style = x ~ style(color = ifelse(x, "green", "red")),
    x ~ icontext(ifelse(x, "ok", "remove"), ifelse(x, "Yes", "No"))),
    `Citation Updates`=formatter("span",
    style = x ~ style(color = ifelse(x, "green", "red")),
    x ~ icontext(ifelse(x, "ok", "remove"), ifelse(x, "Yes", "No"))),
    `Mentions COPE`=formatter("span",
    style = x ~ style(color = ifelse(x, "green", "red")),
    x ~ icontext(ifelse(x, "ok", "remove"), ifelse(x, "Yes", "No"))))
)
```
